Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2025-02-19 src/tex/ms.tex
[showyourwork] overleaf sync

\textcolor{red}{to be adapted... especially the zenodo link\\
Finally, we publicly release all of our code to reproduce the results of this manuscript via GitHub\footnote{URL: {\url{https://github.com/TobiBu/sbi-chempy}}}and refer to Appendix \ref{sec:appendix_code_and_data} for an overview of our code and structure. All our datasets and network weights are publicly available on Zenodo.\footnote{URL: \url{https://zenodo.org/record/8375344}}}

@@

% \begin{figure*}
%     \centering
%     \includegraphics[width=\textwidth]{figures/Nstar_comp_different_prior.pdf}
%     \vspace{-.5cm}
%     \caption{Same as Fig.~\ref{fig:CHEMPY_TNG_N_star_analysis} but for mock data a created with parameters for $\alpha_{IMF}$ and $\log_{10}(N_{Ia})$.}
%     \label{fig:N_star_analysis_different_prior}
%     \script{additional_inference.py}
% \end{figure*}

>>>>

Finally, we publicly release all of our code to reproduce the results of this manuscript via GitHub\footnote{URL: {\url{https://github.com/TobiBu/sbi-chempy}}} and refer to Appendix \ref{sec:appendix_code_and_data} for a more extended overview of our code availability. All our datasets and network weights are publicly available on Zenodo.\footnote{URL: \url{https://zenodo.org/records/14883024}}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/Nstar_comp_different_prior.pdf}
    \vspace{-.5cm}
    \caption{Same as Fig.~\ref{fig:CHEMPY_TNG_N_star_analysis} but for mock data a created with parameters for $\alpha_{IMF}$ and $\log_{10}(N_{Ia})$.}
    \label{fig:N_star_analysis_different_prior}
    \script{additional_inference.py}
\end{figure*}
